Figures

### 2019-04-30 figures/08_exploratory_dotplot.Rmd
show full heatmap

# pheatmap::pheatmap(
#   t(dt_tp),  
#   color = colorRampPalette(RColorBrewer::brewer.pal(n = 7, name =
#                                             "Reds"))(100),
#   cluster_cols = FALSE, cluster_rows = FALSE, 
#   na.col = "grey", 
#   cellheight = 7)
# 
# pheatmap::pheatmap(
#   t(dt_tn),  
#   color = colorRampPalette(RColorBrewer::brewer.pal(n = 7, name =
#                                                       "Reds"))(100),
#   cluster_cols = FALSE, cluster_rows = FALSE, 
#   na.col = "grey", 
#   cellheight = 7)

>>>>

# ----
dt_tp <- dt_sub %>%
  corrr::correlate() %>%
  corrr::shave() %>%
  janitor::remove_empty(c("rows", "cols")) %>%
  mutate_if(is.numeric, round, 2) %>%
  data.frame()

pheatmap::pheatmap(
  t(dt_tp),
  color = colorRampPalette(RColorBrewer::brewer.pal(n = 7, name =
                                            "Reds"))(100),
  cluster_cols = FALSE, cluster_rows = FALSE,
  na.col = "grey",
  cellheight = 7)
# 
# pheatmap::pheatmap(
#   t(dt_tn),  
#   color = colorRampPalette(RColorBrewer::brewer.pal(n = 7, name =
#                                                       "Reds"))(100),
#   cluster_cols = FALSE, cluster_rows = FALSE, 
#   na.col = "grey", 
#   cellheight = 7)
